Topics Causal Inference

### 2024-08-18 documents/paper.tex
Add conclusion.

\documentclass[11pt, a4paper, leqno]{article}
\usepackage{a4wide}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
% \usepackage{float} % Note: incompatible with floatrow
\usepackage{afterpage, rotating, graphicx}
\usepackage{epstopdf}
\usepackage{longtable, booktabs, tabularx}
\usepackage{fancyvrb, moreverb, relsize}
\usepackage{eurosym, calc}
% \usepackage{chngcntr}
\usepackage{amsmath, amssymb, amsfonts, amsthm, bm}
\usepackage{caption}
\usepackage{mdwlist}
\usepackage{xfrac}
\usepackage{setspace}
\usepackage[dvipsnames]{xcolor}
\usepackage{subcaption}
\usepackage{minibox}
% \usepackage{pdf14} % Enable for Manuscriptcentral -- can't handle pdf 1.5
% \usepackage{endfloat} % Enable to move tables / figures to the end. Useful for some
% submissions.
\DeclareMathOperator{\E}{E}
\usepackage{multirow}
\usepackage{threeparttable}
\usepackage[capposition=top]{floatrow}

@@

\section{Introduction}
Estimating treatment effects has become a standard practice in applied econometris.
Also, increasingly large datasets are utilized to investigate systematic heterogeneity.
While this has the potential to increase our understanding of say the heterogneous effects of public policies,
from a methodological perspective large datasets with many covariates come at the risk of increased researchers discretion.
In this case, machine learning methods to systematically explore heterogeneity can be helpful to ``tie the researchers hands''.
Furthermore, in high-dimensional settings with a potentially large number of irrelevant covariates, regularization built-in to many machine learning methods is required to deliver useful results.
However, one concern is that many machine learning methods, like the very popular causal forests proposed in~\cite{wager2018estimation}, to estimate conditional average tretment effects rely on a low-dimensional structure of the conditional effects.
Another approach proposed in~\cite{chernozhukov2023genml} is to only estimate low-dimensional features of conditional effects but utilizing machine learning methods in a first-step prediction exercise.
The current paper investigates the performance of these two approaches for data generating processes both with low- and high-dimensional conditional treatment effect structures.

@@

\section{Conclusion}

\begin{itemize}
    \item Main difficulty: Informative DGP
    \item Think of criterion relevant for decision
    \item Computation power/time to run simulations
    \item Combine WGAN and analytical CATE structure; still need to justify this.
\end{itemize}

>>>>

\documentclass[11pt, a4paper, leqno]{article}
\usepackage[margin=1in]{geometry}

% \usepackage{a4wide}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
% \usepackage{float} % Note: incompatible with floatrow
\usepackage{afterpage, rotating, graphicx}
\usepackage{epstopdf}
\usepackage{longtable, booktabs, tabularx}
\usepackage{fancyvrb, moreverb, relsize}
\usepackage{eurosym, calc}
% \usepackage{chngcntr}
\usepackage{amsmath, amssymb, amsfonts, amsthm, bm}
\usepackage{caption}
\usepackage{mdwlist}
\usepackage{xfrac}
\usepackage{setspace}
\usepackage[dvipsnames]{xcolor}
\usepackage{subcaption}
\usepackage{minibox}
% \usepackage{pdf14} % Enable for Manuscriptcentral -- can't handle pdf 1.5
% \usepackage{endfloat} % Enable to move tables / figures to the end. Useful for some
% submissions.
\DeclareMathOperator{\E}{E}
\usepackage{multirow}
\usepackage{threeparttable}
\usepackage[capposition=top]{floatrow}

@@

\section{Introduction}
Estimating treatment effects has become a standard practice in applied econometrics.
Also, increasingly large datasets are utilized to investigate systematic heterogeneity.
While this has the potential to increase our understanding of say the heterogneous effects of public policies,
from a methodological perspective large datasets with many covariates come at the risk of increased researchers discretion.
In this case, machine learning methods to systematically explore heterogeneity can be helpful to ``tie the researchers hands''.
Furthermore, in high-dimensional settings with a potentially large number of irrelevant covariates, regularization built-in to many machine learning methods is required to deliver useful results.
However, one concern is that many machine learning methods, like the very popular causal forests proposed in~\cite{wager2018estimation}, to estimate conditional average tretment effects rely on a low-dimensional structure of the conditional effects.
Another approach proposed in~\cite{chernozhukov2023genml} is to only estimate low-dimensional features of conditional effects but utilizing machine learning methods in a first-step prediction exercise.
The current paper investigates the performance of these two approaches for data generating processes both with low- and high-dimensional conditional treatment effect structures.

@@

\section{Conclusion}
One of the main difficulties for extending this project besides computational feasibility is the creation of an informative DGP\@.
While the approach taken above allows to control the dimension of the CATE, the covariate structure is of course highly stylized (no discrete covariates, all uniform, all independent).
I think most promising would be a hybrid approach that combines a WGAN generated DGP for the covariates and treatment assignment, with an analytical treatment effect structure.
This still poses the challenge, however, of coming up with a high-dimensional CATE function that makes sense economically.
Eventually, this all boils down to the question, how high-dimensional and non-sparse our objects of interest really are.
Lastly, when moving to low-dimensional summaries of the CATE functional, it would be useful to have decision-theoretic framework to evaluate.
This would allow to think more systematically about how to trade-off model approximations with statistical performance.
